\begin{abstract}
	This paper studies the 
	%interconnectedness of the 
	sovereign bond yields of 15 emerging markets.
	I overcome common concerns in analyzing these yields, like credit risk and small sample sizes, by using synthetic local currency yield curves to account for credit risk 
	and survey forecasts of economic activity to address the small sample problem.
	I document that bond risk premia in emerging markets is time-varying.
	Moreover, I decompose the nominal yields into an expected future short-term interest rate, a term premium and a credit risk premium.
	I find that 
%	a quarter of the 10-year yield of emerging economies is due to the term premium, more than double the size of the credit risk premium.
%	In fact, 
	the bond yields of emerging markets comove mainly driven by the term premia, 
%	which is more globally connected than the credit risk premia and .
	rather than by the expected short rate or the credit risk premia.
	In fact, the global component of term premia is highly linked to the U.S. term premia, whereas its idiosyncratic component is countercyclical. 
	%Further, U.S. monetary policy shocks mainly affect component(s): 1, 2, 3.
	%Finally, a recent reduction in term premia owes in part to declining inflation uncertainty among emerging markets.
	
	% Find the word count in the terminal: pbpaste | wc -w
	\vspace{0.5cm}
	\noindent \textit{Keywords}: Synthetic yield curves, term premium, credit risk, emerging markets, affine term structure models, international spillovers.
	
	\vspace{0.2cm}
	\noindent \textit{JEL Classification}: E43, F34, G12, G15, H63.
	
	\vfill
	
	\pagebreak
\end{abstract}

%	Local currency bond yields are decomposed into three components.
%	The sovereign yields of emerging markets include a credit risk premium, even for bonds denominated in local currency.
%	Yield curve decompositions applied to advanced economies rely on the no-credit-risk assumption and are thus not well suited for emerging markets.
% The sovereign debt of advanced economies is generally considered free of default risk; this is key in the estimation of their term premia. The risk-free assumption, however, is not appropriate for the sovereign debt of emerging market economies.
% I find that the main component for the 10-year yield of emerging markets is the expected future path of the short-term interest rate, while for advanced economies the main component is the term premium. 
% Further, the evidence shows that both global and domestic factors are important drivers of the term premia in emerging markets.