%\newpage
%\begin{appendices}
\iftoggle{toclinks}{\gototoc}{} % Turn it on/off in packages.tex, command in macros.tex
\iftoggle{cboxes}{	   				  % Turn it on/off in packages.tex
	\begin{boxeditems}
		\item None.
	\end{boxeditems}}{}

\renewcommand\thefigure{\thesection.\arabic{figure}}
\section{A Proxy for Long-Term Inflation Forecasts} \label{sec:trendinf}
\setcounter{page}{1}
\setcounter{figure}{0}

An advantage of the small open economy approach to infer long-term forecasts for the short rate is that, for emerging markets, it only requires data on inflation forecasts, or a proxy in the case of countries with no long-term forecasts available as is the case for Israel and South Africa.

Inflation expectations are hoped to match measures of inflation that exclude unexpected shocks and better reflect the inflation environment. 
Different measures of core inflation exist. 
I use the inflation trend obtained by applying the Hodrick--Prescott filter to the series of realized inflation of each country.

There are two main concerns for using this approach. Namely, the filter is sensitive to the sample period used and the resulting trend can be outside of the target inflation band due to the innate dynamics of the series, which would be at odds with survey data (see figure \ref{fig:wnCPI}). In the case of Israel and South Africa, however, there is no marked upward or downward trend in their inflation during the sample period. 
Therefore, for both countries, trend inflation is calculated for the whole period for which survey data is available for the rest of the countries in the sample, and as long as the resulting trend is within the respective inflation target band.

Figure \ref{fig:CPI_ILSZAR} shows the realized and trend inflation for Israel and South Africa along with those of Malaysia and Thailand, two countries with a similar pattern for inflation (i.e., no marked upward or downward trend) and for which survey data is available. 
The figure shows that trend inflation seems to be a good proxy for the long-term inflation forecasts in Malaysia and Thailand. 
Also, as can be seen in the main text (figure \ref{fig:wnCPI}), 5-year and long-term inflation forecasts follow each other closely, therefore trend inflation is used as the proxy for both the 5-year and the long-term inflation forecasts in the case of Israel and South Africa.

\input{../Figures/Surveys/CPI_ILSZAR}


\renewcommand\thefigure{\thesection.\arabic{figure}}
\section{Connectedness of Yields} \label{sec:dyindex}
\setcounter{figure}{0}

%To some extent, the response of emerging market yields to U.S. monetary policy shocks depends on how integrated are LC bonds to the global financial markets. This requires to answer the question of how connected are the sovereign yields of emerging markets.
%One way to address this question is to pool all yields together and see whether there is a global-level factor, associated with the first principal component.
%A global factor explains more than 90\% of the variation in the yields of advanced economies, consistent with \cite{DahlquistHasseltoft:2016}, whereas it only explains around 50\% of the variation in the yields of emerging markets or their components. This suggests that the emerging market yields are not as connected among themselves as the yields of advanced economies.
%A global factor explains around 40\% of the variation of all the three components of yields in EMs.
%For AEs, in contrast, a global factor explains 90\% of the variation in the expected short rate and 80\% in their term premia. 

An alternative approach to rolling correlations for assessing the comovement of yields is the connectedness index of \cite{DieboldYilmaz:2014}. 
The index assesses shares of forecast error variation in a country's bond market due to shocks arising elsewhere.\footnote{ Following \cite{ACDM:2019} and \cite{BostanciYilmaz:2020}, I compute the index  using a VAR(1), with a forecast horizon of 10 days and a rolling window of 150 days for the daily changes of yields.} 
It ranges between 0 and 100\%, higher numbers indicate a higher degree of comovement. 
Figure \ref{fig:dy_index_ts} exhibits the same patterns seen using rolling correlations (cf. figure \ref{fig:rolling_ts}).

Figure \ref{subfig:dyindex10ynomsyn} compares the index for the nominal and synthetic yields of emerging markets with the nominal yields of advanced economies. 
The relatively low connectedness among the yields of emerging markets supports estimating the term structure models for their yield curves separately rather than jointly.
More generally, the evidence of highly connected yields in advanced economies and low connected yields in emerging markets is consistent with global bond markets operating under a core-periphery structure, in which the bond markets of advanced economies constitute the (highly interconnected) core and those of emerging markets represent the (less connected) periphery who are in turn connected to the network mainly through countries in the core.\footnote{ The core-periphery structure has been shown to be a good description of different networks in economics and finance. \cite{CvP:2014}, for example, show that the interbank market operates under such a structure.} 
According to this view, shocks to emerging market yields are mainly idiosyncratic---reflected in less comovement among themselves---so what matters for them are not spillovers originating in other emerging markets but in advanced economies.

Figure \ref{subfig:dyindex10ydcmp} shows the connectedness index for the components of emerging market yields. 
The connectedness of all three components is similar, although the expected future short rate has been slightly more connected over the sample period.\footnote{ \cite{ACDM:2019} show that the increase in the connectedness among the yields of advanced economies has been driven by an increase in the connectedness of their term premia.} 
This suggests that the monetary stance of some emerging markets tends to be aligned. 
Notice that figure \ref{subfig:dyindex10ynomsyn} shows that the level of the index for synthetic yields tends to be higher than that for nominal yields, which suggests that the credit risk component is more idiosyncratic.

%The role of a global factor seems to be different throughout the yield curve.
%Diebold-Yilmaz index for 2Y and 10Y to test Obsfeld vs K-O and whether some sections of the curves are more connected than others.
%\cite{Obstfeld:2015} shows that the effects of the global financial cycle are different at the short than at the long end of the yield curve. In particular, he argues that long-term bonds are more globally connected than short term ones. On the other hand, \cite{Kalemli-Ozcan:2019} argues that short-term yields suffer more the effects of global influences.
%When yields are separated by maturity, a global factor explains around 50\% of the variation in the 1-year yields of EMs, compared to 90\% for AEs. For the 10-year yields, a global factor explains around 60\% of the variability in EMs, relative to 95\% in AEs. 
%In sum, the role of a global component is larger for long-term yields and its components. The connectedness of the short end of the yield curves is similar between advanced and emerging markets. The difference in connectedness between the two groups of countries is therefore driven by the medium and long end of their yield curves. Although foreign participation in LC bond markets has increased, it is still mostly held by local investors, especially medium- and longer-term bonds as suggested by figure \ref{fig:dy_index_ts}, 
%emerging markets are far from being fully integrated in the global financial markets and are therefore more responsive to local factors.

\input{../Figures/Estimation/dy_index_ts}
\input{../Figures/Estimation/dyindex10y} 
\newpage

%---------------------------------------------------------------
% Figures and Tables
%---------------------------------------------------------------
\renewcommand{\thetable}{\thesection.\arabic{table}}
\section{Supplementary Tables} \label{sec:AppTables}
\setcounter{table}{0}

\vspace{1.5cm}
\input{../Tables/ycdcmp5y} 
\input{../Tables/ycdcmp1y} 
\input{../Tables/mpsstats} 
\vspace{3cm}

\newpage

\renewcommand\thefigure{\thesection.\arabic{figure}}
\section{Supplementary Figures} \label{sec:AppFigures}
\setcounter{figure}{0}

\begin{landscape}
	\input{../Figures/Estimation/crc_cds_EM}
	\input{../Figures/Estimation/bsl_tp_CI_10y_V1}
	\input{../Figures/Estimation/bsl_cr_CI_10y_V1}
	\input{../Figures/Estimation/bsl_tp_ts}
\end{landscape}

\begin{landscape}
\input{../Figures/LPs/Latex/LP_US_Shk} 
\input{../Figures/LPs/Latex/LP_US_Shk_Path}
\input{../Figures/LPs/Latex/LP_EM_Shk_Path}
\end{landscape}

\input{../Figures/LPs/Latex/LP_RHO} 

\begin{landscape}
	\newpage
\end{landscape}

%\end{appendices}